DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2023-05-30 manuscript/manuscript.Rmd
add Brian's edits

Completing a phylogeny using a stochastic birth-death polytomy resolver and a backbone taxonomy is a common practice in scientific publications: @Jetz2012, created a chronogram of all 9, 993 bird species, where 67% had molecular data and the rest was simulated; @rabosky2018inverse created a chronogram of 31, 536 ray-finned fishes, of which only 37% had molecular data; @smith2018constructing constructed a chronogram of 353, 185 seed plants where only 23% had molecular data. These stochastically resolved chronograms return diversification rates estimates that appear less biased than those estimated from their incompletely sampled counterparts, even with methods that account for missing lineages by using sampling fractions [@cusimano2012new; @chang2020estimating], but can also introduce spurious patterns of early bursts of diversification [@cusimano2010slowdowns; @sun2020estimating].

>>>>

Completing a phylogeny using a stochastic birth-death polytomy resolver and a backbone taxonomy is a common practice in scientific publications: @Jetz2012, created a chronogram of all 9,993 bird species, where 67% had molecular data and the rest was simulated; @rabosky2018inverse created a chronogram of 31,536 ray-finned fishes, of which only 37% had molecular data; @smith2018constructing constructed a chronogram of 353,185 seed plants where only 23% had molecular data. These stochastically resolved chronograms return diversification rates estimates that appear less biased than those estimated from their incompletely sampled counterparts, even with methods that account for missing lineages by using sampling fractions [@cusimano2012new; @chang2020estimating], but can also introduce spurious patterns of early bursts of diversification [@cusimano2010slowdowns; @sun2020estimating].
